CdGF_aucrf

### 2016-09-22 code/CdGF_AUCRF.Rmd
improve random validation with boruta

#### Random - 10-fold Cross validated - 10 repetitions
ran_aucrf_data <- cbind(Euth_Early = factor(sample(Predict_early_euth_df$Euth_Early, 
                                                     nrow(Predict_early_euth_df))),
                             Predict_early_euth_df[,rf_early_aucrf$Xopt])
ran_cv10f_aucs <- c()
ran_cv10f_all_resp <- c()
ran_cv10f_all_pred <- c()
for(j in 1:iters){
  sampling <- sample(1:nrow(ran_aucrf_data),nrow(ran_aucrf_data),replace=F)
  ran_cv10f_probs <- rep(NA,nrow(ran_aucrf_data))
  for(i in seq(1,nrow(ran_aucrf_data),5)){
    train <- ran_aucrf_data[sampling[-(i:(i+4))],]
    test <- ran_aucrf_data[sampling[i:(i+4)],]
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    ran_cv10f_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  ran_cv10f_roc <- roc(ran_aucrf_data$Euth_Early~ran_cv10f_probs)
  ran_cv10f_all_pred <- c(ran_cv10f_all_pred, ran_cv10f_probs)
  ran_cv10f_all_resp <- c(ran_cv10f_all_resp, ran_aucrf_data$Euth_Early)
  ran_cv10f_aucs[j] <- ran_cv10f_roc$auc
}
ran_cv10f_roc <- roc(ran_cv10f_all_resp~ran_cv10f_all_pred)

@@

@@

#### leave-one-cage-out
LOcO_df <- cbind(cage_id = sample(meta_file[meta_file$day %in% 0, 'cage_id'],
                                  nrow(Validate_early_euth_df)),
                 Validate_early_euth_df[ , c('Euth_Early', rf_early_aucrf$Xopt)])
cage_list <- as.character(unique(LOcO_df$cage_id))

>>>>

#### Random - 10-fold Cross validated - 10 repetitions

ran_cv10f_aucs <- c()
ran_cv10f_all_resp <- c()
ran_cv10f_all_pred <- c()
for(j in 1:iters){
  set.seed(j)
  ran_aucrf_data <- cbind(Euth_Early = factor(sample(Predict_early_euth_df$Euth_Early, 
                                                     nrow(Predict_early_euth_df))),
                             Predict_early_euth_df[,rf_early_aucrf$Xopt])
  set.seed(seed)
  sampling <- sample(1:nrow(ran_aucrf_data),nrow(ran_aucrf_data),replace=F)
  ran_cv10f_probs <- rep(NA,nrow(ran_aucrf_data))
  for(i in seq(1,nrow(ran_aucrf_data),5)){
    train <- ran_aucrf_data[sampling[-(i:(i+4))],]
    test <- ran_aucrf_data[sampling[i:(i+4)],]
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    ran_cv10f_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  ran_cv10f_roc <- roc(ran_aucrf_data$Euth_Early~ran_cv10f_probs)
  ran_cv10f_all_pred <- c(ran_cv10f_all_pred, ran_cv10f_probs)
  ran_cv10f_all_resp <- c(ran_cv10f_all_resp, ran_aucrf_data$Euth_Early)
  ran_cv10f_aucs[j] <- ran_cv10f_roc$auc
}
ran_cv10f_roc <- roc(ran_cv10f_all_resp~ran_cv10f_all_pred)

@@

```{r}

# boruta feature selection
random_boruta <- read.table('~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/random_rf_features_boruta.txt', sep = '\t')
random_boruta <- random_boruta[, c('normHits', 'decision')]
random_boruta$OTU <- rownames(random_boruta)
```

When randomly redistributing the Early Euthnization classification to the Day 0 commnunities, Boruta does not select any OTUs  
Summing the OTU decisions from 100 iterations of randomly assigning classifications run in Boruta with 100 iterations produces:
`r summary(random_boruta$decision)`
Of all the Confirmed OTUs there are `r length(unique(random_boruta$OTU[random_boruta$decision == 'Confirmed']))` unique OTUs
Of all the Tentative OTUs there are `r length(unique(random_boruta$OTU[random_boruta$decision == 'Tentative']))` unique OTUs
Furthermore, there is no overlap in the identified OTUs, since there are `r length(unique(random_boruta$OTU[random_boruta$decision %in% c('Tentative', 'Confirmed')]))` unique OTUs.  
Thus, no OTUs are able to create a model with out the specific pattern of observed disease severity.

@@

#### leave-one-cage-out
LOcO_df <- cbind(cage_id = Predict_df$cage_id,
                 Validate_early_euth_df[ , c('Euth_Early', rf_early_aucrf$Xopt)])
cage_list <- as.character(unique(LOcO_df$cage_id))
